\subsection{Objectives}

\begin{longtable}{|p{1cm}|p{4cm}|p{4cm}|p{3cm}|p{1cm}|} 
    \hline
        No & Objective & Evaluation & Client Feedback & Timestamp \\ 
    \hline
        1.1
        & 
        A RISC (Reduced Instruction Set Computer) design philosophy. 
        &
        & 
        4:27-5:10
        \\
  \hline
        1.2 
        & 
        A Von Neuman computer architecture where data and instructions are stored in the same memory. 
        & 
        & 
        20:25-21:00
        \\
  \hline
        1.3 
        &  
        My Instruction Set should utilize 3 address operands standards.
        & 
        & 
        5:10-5:35
        \\
  \hline
        1.4 
        & 
        Branch and call instructions should calculate offsets from labels in the source code. 
        & 
        & 
        5:35-6:05
        \\
  \hline
        1.5 
        & 
        Macro instructions to perform common tasks that are not otherwise specified in the ISA. 
        &
        & 
        6:05-6:25, 9:05-10:53
        \\
    \hline
        1.6 
        & 
        A set of registers broad enough to minimse memory access. 
        &
        & 
        6:25-6:43, 7:30-9:05
        \\
    \hline
        1.7 & 
        A CPU word length of 16-bits. &
        &
        6:43-6:56
        \\
    \hline
        2.1 & 
        C standard syntax with semi colons and braces rather than indentation. &
        & \\
    \hline
        2.2 & 
        The programming language should be statically typed. &
        & \\
    \hline
        2.3 & 
        The language should support a procedural programming paradigm. &
        & \\
    \hline
        2.4 & 
        My language should support references and pointers to variables in memory. & 
        & \\
    \hline
        2.5 & 
        The compiler should produce relevant error messages, pointing out the position in source code if relevant. &
        &\\
        \\
    \hline
        3.1 & 
        The Virtual Machine should include a graphical display showing the contents of VRAM. &
        & 
        \\
    \hline
        3.2 & 
        The Virtual Machine should include a togglable debugger. &
        & \\
        \hline
\end{longtable}